\section{Conclusion}
% What specifically do we want to make.
% Why we want to make it
% How this will be applicable
% How it can be improved

The goal of this project was to create a proof of concept for a platform that can prototype multiple different robot arms. We feel that we accomplished the most of the goals defined in the Acceptance Criteria through our proof of concept. This project spanned a broad swathe of engineering disciplines and as such required lots of work in each of the three "pillars of robotics". Mechanical engineering, electrical engineering and computer science all played important roles in the design and implementation of our robotic arm. We made use of our respective backgrounds in this area in addition to a large amount of self-study required to fully realize our goal. \\
\newline
\noindent From the start of this project, we knew that it would not be an trivial accomplishment to make a modularly reconfigurable robot arm. In this project, we defined the goals that we wanted to achieve and tried to clearly lay them out in the Acceptance Criteria. Very few of our ideas came from external sources because we decided to create a new concept for robot arms. It was clear to us at the beginning of the project that if we were to meet this goal, we would have to approach many complex engineering problems and solve them using innovative and creative methods. In the end, we were able to make our arm, but not without running into many errors which can be expected with a project of this scope. There were a few roadblocks which impeded progress and led to executive decisions to change how we approached certain problems. Principal amongst these was a project redesign in response to a change in project administration late A term. This redesign was not just a test of our dedication to the project but our dedication to our goals. It turned out that due to the shortened time span which we had to complete this project, we had to rethink some goals and scale others back so that they were achievable. \\
\newline
\noindent In possible future iterations of this project, we would urge teams who decide to take up this project to follow our goals outlined in the Acceptance Criteria. We spent a long time on these goals in order to make them fully encapsulate what we want as an end-deliverable for the project.  All of this careful planning gave us a good outline for what we should be accomplishing in the project and therefore should be utilized by subsequent iterations to begin working more quickly. Overall, we would urge teams to expand more in the mechanical aspect of the arm. Instead of undoing all of the work we did to create such a robust and simple joint control board, it would be more beneficial to the project to use the current electrical system and modify the parts of the arm that were not made by us. There is also quite a bit of room to expand in the software application area, implementing more types of controls and making the GUI more intuitive and easy to use. By avoiding our mistake of spending so much time defining what we wanted out of the project, subsequent teams should pick up where we left off and make use of the work we did over this past year.  


%thread
%comms protocol
%design PCB
%schedule on RTOS
%
%
%
%design an educational platform
%We made a platform that could, in principle, be used for education
%Structure of final project met original goals
%Staffing circumstances and time constraints made achieving the original goal difficult, but we did in fact get a proof of concept out there. It is achievable
%
%CAD -> 3D print, iterate
%
%UML -> code, iterate
%
%Design + read datasheets -> breadboard -> miniPCB -> full PCB
%
%Enormous roadblocks:    CAN. HID. Project redesign. Linux / Windows compatibility: solidworks doesn't run on linux. Code written on Windows for Tiva didn't work on Linux. 3D printer's tolerance needed to be iterated many times. 3D printer settings needed to be rewritten from scratch.
%
%Turns out joint boards need to be powered from USB port, not just motor & logic power. The fix is to power the boards at 5 volts on the logic line.
%
%Embedded code led to problems that couldn't be solved by thinking, but rather by brute force elimination of possible root causes
%
%Debugging matrix
%
%
%You design the project. Hardest kind of MQP. You tell the advisors what you're doing and then you do it. When you hit a roadblock it's not just a question of how can we overcome it, but also a question of, isit worthwhile to persevere or should we aim for more achievable goals?
%
%
%The Engineering Process: Research. Plan. Design. Build. Test. Iterate.
%
%At its heart, this project embodied the three pillars of Robotics Engineering. We got to use so many skills. In the end we made something that we feel is a valid proof of concept.
%
%We spent a significant amount of time defining project deliverables (Outlined in Appendix \ref),  but due to changes and project organization, the goals had to be revised.
%
%
%
%We achieved many of our basic goals. There is still much to be done to accomplish the full scope of the original project narrative. Future iterations of this project could focus on adding higher level functionality to our platform. An example would be utilizing the torque sensing capability or other sensors to add additional control methods, such as torque control and gravity compensation, or maybe even velocity control.
