\section{Introduction} 
% Section outline:
% Overall summary of project - ~1 sentence per major goal
% ~1 Paragraph for each major goal
% Paragraph at end describing what is in this document

The goal of this project is to create a adaptable control system whose purpose is to drive a variety of robotic arms. To prove the usefulness of our system, we plan on taking an existing arm from the RBE 3001 course and retrofit it with our control system.  In addition to this, we will modify the existing arm to include an interchangeable link on the end of our arm, controlled by our system. To interface with our system, we will create a GUI for easy configuration and basic control of the arm. The base will communicate with a computer running control code either through the software application or code library. \\
\newline
The existing RBE 3001 arm currently has its own central control system. We aim to remove this and replace it with our own distributed one. To accomplish this, we will design a motor control board that communicates with a base controller.  Additionally, we will design and implement a new link on the arm. This new link will be interchangeable and implement our control board. \\
\newline
We will create a software application to interface with a constructed arm. The user will input how they have constructed their arm into this application and then be able to do some simple control. Another feature of this application will be the ability to record a series of poses for the arm to perform. In addition to this software, we will also create some programming libraries to allow users to control the arm with an actual program. \\
\newline
In this document, we will outline some existing robot arms and highlight the differences between these arms and our arm kit. We then discuss what work there is to be done on this project. After discussing the work to be done, we will state how this work will satisfy the capstone design requirements for each of the three disciplines represented by our group members. Then, we state the constraints we expect going forward with this project. Next, the acceptance criteria for any deliverables at the end of this project will be outlined. Finally, we will state an estimated timentire line for this project.